\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=1in]{geometry}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

Elmahdi Harchi\\
Montr\'eal, QC\\
Tel.: +1 343-254-6991\\
Email: \href{mailto:mehdi.hr111@gmail.com}{mehdi.hr111@gmail.com}

September 10, 2025\\

Desirae Munro — Branch Manager / Assistant Director\\
Wheatland Regional Library\\
806 Duchess Street\\
Saskatoon, SK  S7K 0R3\\
\href{mailto:branchmanager@wheatland.sk.ca}{branchmanager@wheatland.sk.ca}

Subject: Application — Computer Technician (Part-time, Permanent)

Dear Ms. Munro,

I am writing to apply for the Computer Technician position (Part-time, Permanent) with Wheatland Regional Library. I am a bilingual (French/English), detail-oriented IT professional and recently graduated with a DEC in Computer Programming (Coll\`ege La Cit\'e, 2025). I am motivated by public service and collaborative work, and I would welcome the opportunity to support your region’s technology operations and service delivery.

In my recent roles, I provided front-line technical support, documented requests and resolutions in a ticketing system, and followed defined procedures to ensure quality and consistency. I set up and maintained end-user devices, installed software and updates, performed basic network diagnostics, supported printers/peripherals, and assisted with inventory organization and equipment check-in/out. I also created clear, step-by-step guides and contributed to a small internal knowledge base to assist colleagues and end users.

I am comfortable working across Windows environments and Microsoft 365, and I have foundational exposure to web technologies (HTML/CSS/JavaScript) from academic and project work—experience that can support website content updates and maintenance as required. I learn new systems quickly and am eager to grow into areas central to your posting, including virtualized environments (e.g., Hyper-V), licensing administration, Fortinet devices, SQL-backed applications, and broader network infrastructure tasks. I am organized, attentive to detail, and able to meet deadlines while communicating clearly with staff and stakeholders across multiple sites.
I am comfortable working across Windows environments, Microsoft 365, and Google Workspace, and I have foundational exposure to web technologies (HTML/CSS/JavaScript) from academic and project work—experience that can support website content updates and maintenance as required. I learn new systems quickly and am eager to grow into areas central to your posting, including Hyper-V and virtual servers, licensing administration, Fortinet firewalls/devices, SQL-backed applications, and broader network infrastructure tasks. I am organized, attentive to detail, and able to meet deadlines while communicating clearly with staff and stakeholders across multiple sites.

The responsibilities outlined in your posting—coordinating IT functions region-wide, maintaining computers/servers and network connections, assisting with training programs, supporting the library’s web presence, and participating in provincial committees—align strongly with my strengths in documentation, customer service, teamwork, and continuous learning. I am prepared to lift and move equipment safely, follow established policies and procedures, and maintain a clean, reliable operational environment. I am open to relocating to Saskatoon, SK, can provide a current acceptable Criminal Record Check, hold a valid driver’s license with an exemplary driving record, can drive throughout the region as required, and am bondable.

I would be grateful for the opportunity to discuss how I can contribute to Wheatland Regional Library’s mission. Thank you for your time and consideration. I am available at your convenience and can be reached at +1 343-254-6991 or by email at mehdi.hr111@gmail.com.

Sincerely,\\[10pt]
Elmahdi Harchi

\end{document}
