\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=1in]{geometry}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

Elmahdi Harchi\\
Montréal, QC\\
Tel: +1 343-254-6991\\
Email: \href{mailto:mehdi.hr111@gmail.com}{mehdi.hr111@gmail.com}

September 9, 2025\\

Hiring Manager\\
Randstad Canada\\
Barrie, ON

Subject: Application — Customer Service / Counter Sales (Warehouse Support)

Dear Hiring Manager,

I am an energetic, organized, and customer service–oriented professional ready for an immediate interview and start. With 1+ year of front-line customer service experience in fast-paced environments (front counter and hospitality) and strong computer skills (Microsoft Office, accurate data entry, professional phone/email), I am excited to contribute to your well-known supplier in Barrie. I am bilingual (French/English) and open to relocating to Barrie for this opportunity.

Highlights of my fit for your role:
- Customer Service: Greet customers by phone, email, and in person; listen, clarify needs, and resolve inquiries with a positive, solutions-focused attitude.
- Order Intake & Data Entry: Accurately process orders, complete computer input, and document follow-ups; experienced with POS and comfortable learning new systems quickly.
- Warehouse Support & Scanning: Familiar with scanning workflows and quick to learn RF scanners; ready to support picking/packing and inventory tasks as needed.
- Fast-Paced Teamwork: Thrive in high-volume settings, multitask effectively, and maintain a clean and safe workspace while meeting deadlines.
- Availability: Day shift Monday–Friday 7:00 a.m.–4:30 p.m.; able to rotate Saturdays (7:00–12:00) during summer; immediate start.

I’m drawn to your high-energy team and the opportunity for long-term growth and advancement. I would welcome the chance to discuss how I can help deliver top-notch service to your customers and keep the products flowing.

Thank you for your time and consideration. I look forward to speaking with you.

Sincerely,\\[10pt]
Elmahdi Harchi

\end{document}
